\vspace{-12pt}
\section{References}

\renewcommand{\labelenumi}{[\theenumi]}

\begin{small} %footnotesize
\begin{enumerate}[leftmargin=*]
  \itemsep 2pt
  \item \textbf{Pei-Yu (Peggy) Chi}, Sally Ahn, Amanda Ren, Mira Dontcheva, Wilmot Li, and Björn Hartmann. 2012. MixT: automatic generation of step-by-step mixed media tutorials. In Proceedings of \emph{UIST '12}: ACM Symposium on User Interface Software and Technology.
  \item \textbf{Pei-yu (Peggy) Chi}, Bongshin Lee, and Steven M. Drucker. 2014. DemoWiz: re-performing software demonstrations for a live presentation. In Proceedings of \emph{CHI '14}: ACM Conference on Human Factors in Computing Systems.
  \item \textbf{Pei-Yu (Peggy) Chi}, Joyce Liu, Jason Linder, Mira Dontcheva, Wilmot Li, and Björn Hartmann. 2013. DemoCut: generating concise instructional videos for physical demonstrations. In Proceedings of \emph{UIST '13}: ACM Symposium on User Interface Software and Technology.
  \item \textbf{Pei-Yu (Peggy) Chi}, Mira Dontcheva, Wilmot Li, Daniel Vogel, Bj\"orn Hartmann. Generating illustrated movement instructions from physical demonstrations. \emph{In preparation}.
  \item \textbf{Pei-Yu (Peggy) Chi} and Henry Lieberman. 2011. Intelligent assistance for conversational storytelling using story patterns. In Proceedings of \emph{IUI '11}: ACM Conference on Intelligent User Interfaces.
  \item \textbf{Pei-Yu (Peggy) Chi} and Henry Lieberman. 2011. Raconteur: integrating authored and real-time social media. In Proceedings of \emph{CHI '11}: ACM Conference on Human Factors in Computing Systems.
  \item \textbf{Pei-Yu (Peggy) Chi} and Yang Li. 2015. Weave: Scripting cross-device wearable Interaction. In Proceedings of \emph{CHI '15}: ACM Conference on Human Factors in Computing Systems.
  \item \textbf{Pei-Yu (Peggy) Chi}, Yang Li, and Björn Hartmann. 2016. Enhancing cross-device interaction scripting with interactive illustrations. To appear at \emph{CHI '16}: ACM Conference on Human Factors in Computing Systems.
\end{enumerate}
\end{small}
