%!TEX root = ../thesis.tex
\begin{acknowledgements}

I would first like to thank my advisor, Bj\"orn Hartmann, for opening up research opportunities and collaborations that led me to where I am today.
%
Bj\"orn's full support of my interest in video, which I derived from my previous work at the MIT Media Lab, introduced me to interactive instructional design that I truly enjoy exploring. Working with Bj\"orn made five years short as ideas emerged quickly in every discussion. I thank him for his encouragement to pursue my four summer internships that led me to my full-time position. I must mention that it was fun biking together at the Google campus, where we brainstormed about which caf\'{e} to visit, and of course, research topics.
% : computational instructional design
I also want to thank Eric Paulos, Kyle Steinfeld, and Marti Hearst on my qualifying exam and thesis committees for their valuable and encouraging feedback, which drove my work forward as a whole.

I feel so grateful to be able to work closely with researchers from outside UC Berkeley over the last five years: soon after joining Berkeley, I began working with Mira Dontcheva and Wilmot Li at Adobe Research. This evolved into our first exciting collaboration, and eventually three fruitful projects. Their thoughtful, patient, and cheerful guidance indirectly encouraged me to join industrial research.
%
Steven M. Drucker and Bongshin Lee at Microsoft Research sparked my interest in visualization under their mentorship.
%
Daniel Vogel, while an interviewee at first, became a key author on one of my works, which was very fortunate for me.
%
Finally, Yang Li at Google Research expanded my view to another research topic, programming tools for cross-device interaction. My work with Yang and Bj\"orn led to a best paper award at CHI.

This dissertation could not have been completed without the support from the many students who collaborated with me in my research: Sally Ahn, Amanda Ren, Joyce Liu, Jason Linder, Derrick Cheng, and Taeil Kwak. I wish to extend thanks to members of my research groups at the Berkeley Institute of Design, Visual Computer Lab, and EECS: Andrew Head and Amy Pavel for their continuous research support, Fu-chung Huang, Nicholas Kong, Kenghao Chang, Tsung-hsiang Chang, and Chung-wei Lin for advice as fresh PhDs, Valkyrie Savage and Shiry Ginosar for making the best and very first ``b-crew'', Steven Rubin for his expertise in audio research, William McGrath for brainstorming about AR authoring tools, and Cesar Torres and Tim Campbell for being part of my ``research family'' studying tutorials.

I thank the university and my industry collaborators for their encouragement in support. In particular, UC Berkeley and Google have graciously supported my studies through a Fellowship for Graduate Study and a PhD Fellowship. My longtime mentors Hao Chu, Robin Chen, Jimmy Lin, and Henry Lieberman have guided me in navigating the research world.

Finally, this dissertation is dedicated to my dear family: my parents, Rock Chi and Joanna Chen, my sister, Hsin-yu Chi, my husband, Senpo Hu, and my adorable daughter, Marissa Hu. I thank them for their tremendous love and support.

\end{acknowledgements}
