%!TEX root = ../thesis.tex
% \title{Kinectograph: Body-Tracking Camera Control for Self-Directed Demonstration Videos}
\chapter{Kinectograph: Body-Tracking Camera Control}
\label{chapter_kinectograph}

A large community of users creates and shares how-to videos online. Many of these videos show demonstrations of physical tasks, such as fixing a machine or demonstrating dance steps. It is often difficult for the authors of these videos to control camera focus, view, and position while performing their tasks.

To help instructors produce videos, in this chapter, we introduce Kinectograph\footnote{This work was published at CHI 2013~\cite{Cheng:2013:BCC:2468356.2468568}.}, a recording device that automatically pans and tilts to follow specific body parts, e.g., hands, of a user in a video with lightweight control. It utilizes a Kinect depth sensor to track skeletal data and adjusts the camera angle via a 2D pan-tilt gimbal mount. Users configure Kinectograph through a tablet application with real-time video preview. We conducted a preliminary evaluations to test the usability of Kinectograph's control interface. All of the participants successfully created instructional videos without assistance. The initial findings suggested that Kinectograph enables instructors to focus on performing their demonstrations, while giving them sufficient camera control at recording time.

\input{\kinectograph/introduction}

\input{\kinectograph/workflow}

\input{\kinectograph/system}

\input{\kinectograph/implementation}

\input{\kinectograph/evaluation}

\section{Conclusion}
We presented Kinectograph, a new device that provides automatic and user-controlled camera orientation. We showed initial evidence of its effectiveness for self-recording demonstration tasks. We see applications of Kinectograph beyond the domain of instructional video and are investigating the opportunities of rich tracking information for video recording and editing in general.

%\section{Note on prior submission}
%This paper is based on a non-archival poster accepted for publication at CHI 2013. The prior version used a substantially different user interface and %backend. We also expanded the evaluation of our system in this submission.

% and whether the user's actions with the UI produced the expected result. we aimed to confirm that our features did work well and that the UI was easy enough to use to perform an assigned task.}

% Balancing columns in a ref list is a bit of a pain because you
% either use a hack like flushend or balance, or manually insert
% a column break.  http://www.tex.ac.uk/cgi-bin/texfaq2html?label=balance
% multicols doesn't work because we're already in two-column mode,
% and flushend isn't awesome, so I choose balance.  See this
% for more info: http://cs.brown.edu/system/software/latex/doc/balance.pdf
%
% Note that in a perfect world balance wants to be in the first
% column of the last page.
%
% If balance doesn't work for you, you can remove that and
% hard-code a column break into the bbl file right before you
% submit:
%
% http://stackoverflow.com/questions/2149854/how-to-manually-equalize-columns-
% in-an-ieee-paper-if-using-bibtex
%
% Or, just remove \balance and give up on balancing the last page.
%
